Parallel Monte Carlo Synthetic Acceleration Methods for Discrete Transport Problems

### 2013-09-04 doc/dissertation/presentation/defense.tex
small updates to presentation

  \begin{itemize}
  \item New algorithms required to leverage new computational
    resources
    \begin{itemize}
    \item Tremendous computational resources are required with
      $O(\sn{1}{9})$ element meshes and $O(100,000)+$ cores used today
      for neutronics and fluid problems (Evans,2010)(Pawlowski,2012)
    \end{itemize}
    \bigskip
  \item Necessary to determine applicability to reactor physics and
    potential performance improvements before moving forward with
    other work
    \bigskip
  \item Physics-driven development
    \begin{itemize}
    \item Research applicability and potential improvements to
      neutronics and fluid flow
    \item Offer solutions or a potential path forward for the observed
      issues
    \item Work to improve iterative and parallel performance
    \end{itemize}
  \end{itemize}

@@

  \begin{itemize}
    {\small
    \item Drekar is a production fluid base using Newton methods
      with FAD
      \medskip
    \item MCLS incorporated into Drekar nonlinear scheme to implement
      FANM
      \medskip
    \item Newton-Krylov method with Aztec GMRES used for benchmark
      comparisons
    \item All problems preconditioned with explicit scheme using
      algebraic multigrid (ML) and leveraged some kind of
      globalization (e.g. backtracking) 
    }
  \end{itemize}

@@

      \small{
        \begin{itemize}
        \item Forcing term selection can significantly modify nonlinear
          convergence
        \item Newton-Krylov had larger forcing terms for Re=100,300,500
        \item At Re=700, MCSA histories doubled and RDA fill increased
          from 200 to 300
        \end{itemize}
      }

>>>>

  \begin{itemize}
  \item New algorithms required to leverage new computational
    resources
    \begin{itemize}
    \item Tremendous computational resources are required with
      $O(\sn{1}{9})$ element meshes and $O(100,000)+$ cores used today
      for neutronics and fluid problems (Evans,2010)(Pawlowski,2012)
    \end{itemize}
    \bigskip
    \bigskip
  \item Physics-driven development
    \begin{itemize}
    \item Research applicability and potential improvements to
      neutronics and fluid flow
    \item Offer solutions or a potential path forward for the observed
      issues
    \item Work to improve iterative and parallel performance
    \end{itemize}
  \end{itemize}

@@

  \begin{itemize}
    {\small
    \item Drekar is a production CFD code using Newton methods with
      FAD
      \medskip
    \item MCLS incorporated into Drekar nonlinear scheme to implement
      FANM
      \medskip
    \item Newton-Krylov method with Aztec GMRES used for benchmark
      comparisons
    \item All problems preconditioned with explicit scheme using
      algebraic multigrid (ML) and leveraged some kind of
      globalization (e.g. backtracking) 
    }
  \end{itemize}

@@

      \small{
        \begin{itemize}
        \item Forcing term selection can significantly modify nonlinear
          convergence
        \item Newton-Krylov always had larger forcing terms
        \item At Re=700, MCSA histories doubled and RDA fill increased
          from 200 to 300
        \end{itemize}
      }
